Transparent Changes

### 2022-05-02 scripts/review.Rmd
Update review script

write.csv(extr, "../data/extract/extraction.csv", row.names = FALSE)
```

@@

```{r percentages}
load("../data/review.Rda")
# Remove Douglas bag measurements
ext <- ext[ext$type != "douglas", ]

@@

knitr::kable(purrr::map_dfr(reporting, scales::percent, accuracy = 0.1))

@@

```{r}
library(treemapify)
library(dplyr)

@@

ggplot(ext_count, aes(area = n, fill = proc_combination, label = label, subgroup = subgroup)) +
  geom_treemap(show.legend = FALSE, start = "topleft") +
  geom_treemap_text(reflow = TRUE, place = "centre", start = "topleft")

>>>>

# write.csv(extr, "../data/extract/extraction.csv", row.names = FALSE)
```

@@

```{r percentages}
load("../data/review.Rda")

@@

knitr::kable(purrr::map_dfr(reporting, scales::percent, accuracy = 0.1))
```

@@

```{r}
library(treemapify)
library(dplyr)
library(colorspace)

@@

ggplot(ext_count, aes(area = n, fill = proc_combination, label = label, subgroup = subgroup)) +
  geom_treemap(show.legend = FALSE, start = "topleft") +
  geom_treemap_text(
    color = "black",
    reflow = TRUE, 
    place = "centre", 
    start = "topleft",
    padding.y = grid::unit(1.5, "mm")) +
  scale_fill_manual(
    values = colorspace::lighten(c("#663171", "#ea7428", "#653151", "#0c7156", "#0c7182"), amount = 0.2)
  )
